Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-15 RR_manuscript/Draft_RR.Rmd
♻️ - add notice about auth affiliations
fix to proportion of "reliable effects"

@@

The question arises whether these unique analysis pipelines led to different conclusions. 
`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%).

>>>>

> Authors' affiliations to be added later.

@@

The question arises whether these unique analysis pipelines led to different conclusions. 
`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
Of the 170 critical model coefficients, `r n_effects` were claimed to show a statistically reliable effect (`r round(perc_effects,1)`%).
